---
title: "CSV.GZ Conversion to CSV"
author: "Evan Canfield"
date: "10/31/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Library
The following are library packages used in this analysis.
```{r library}
if (!require(pacman)) {install.packages('pacman')} 
p_load(
    bit64
  , data.table
  , ff
  , feather
  , here
  , janitor
  , R.utils
  , stringr
  , tidyverse
)
```

# Process CSV.GZ Files
The files provided in the MIMIC-III dataset are *csv.gz* files. This file type is a compressed *csv* used for database applications. The purpose of this section is to import the file, clean the files with janitor, and then export as a standard csv file for easier use in this project.

## Import
```{r message=FALSE, eval=TRUE}
note_events <- read_csv(file = here("data/raw_csv.gz/noteevents.csv.gz"))
```

## Clean Column Names With Janitor
```{r clean df, eval=FALSE}
admissions <- clean_names(dat = admissions, case = "snake")

callout <- clean_names(dat = callout, case = "snake")

caregivers <- clean_names(dat = caregivers, case = "snake")

#chartevents <- clean_names(dat = chartevents, case = "snake")

cptevents <- clean_names(dat = cptevents, case = "snake")



d_icd_diagnosis <- clean_names(dat = d_icd_diagnosis, case = "snake")

d_icd_procedures <- clean_names(dat = d_icd_procedures, case = "snake")

d_items <- clean_names(dat = d_items, case = "snake")

d_labitems <- clean_names(dat = d_labitems, case = "snake")
```

## Write To Feather
```{r write_feather, eval=FALSE}
write_feather(x = admissions, path = here("data/raw_feather/admissions.feather"))

write_feather(x = callout, path = here("data/raw_feather/callout.feather"))

write_feather(x = caregivers, path = here("data/raw_feather/caregivers.feather"))

#write_feather(x = chartevents, path = here("data/raw_feather/chartevents.feather"))

write_feather(x = cptevents, path = here("data/raw_feather/cptevents.feather"))

write_feather(x = d_cpt, path = here("data/raw_feather/d_cpt.feather"))

write_feather(x = d_icd_diagnosis, path = here("data/raw_feather/d_icd_diagnosis.feather"))

write_feather(x = d_icd_procedures, path = here("data/raw_feather/d_icd_procedures.feather"))

write_feather(x = d_items, path = here("data/raw_feather/d_items.feather"))

write_feather(x = d_labitems, path = here("data/raw_feather/d_labitems.feather"))
```

## Create list of Files
```{r}
#create list of csv.gz files
file_names_original <- list.files(
  path = here("data/raw_csv.gz"),
  pattern="*csv.gz"
    )

#convert to lower case
file_names <- tolower(file_names_original)

#extract file name from extension
file_names <- gsub("\\..*","", file_names)
```

## Loop for Conversion to Feather
```{r eval=FALSE}
while(i < length(file_names) + 1){
    # Create File Path to Pull csv.gz file
    filepath_read <- paste0(here("data/raw_csv.gz"),"/",file_names_original[i])
     
    # Create file path string to save feather file
    filepath_write <- paste0(here("data/raw_feather"),"/",file_names[i],".feather")

    # Read CSV
    df <- fread(filepath_read)

    # Clean Column Names CSV
    df <- clean_names(dat = df, case = "snake")

    # Write to Feather File
    write_feather(x = df, path = filepath_write)
}
```


