---
title: "MIMIC III Dataset - Structured Data Analysis"
author: "Evan Canfield"
date: "10/31/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Library
The following are library packages used in this analysis.
```{r library}
if (!require(pacman)) {install.packages('pacman')} 
p_load(
    data.table
  , fastDummies
  , feather
  , here
  , Hmisc
  , janitor
  , lubridate
  , R.utils
  , skimr
  , stringr
  , tidyverse
)
```

# Set Seed
```{r}
set.seed(5590)
```


# Import
```{r}
#chartevents <- read_feather(here("data/raw_feather/chartevents.feather"))
#note_events <- read_feather(here("data/raw_feather/noteevents.feather"))

#here::here("data/raw_feather/labevents.feather")

# Lab Results
lab_events <- read_feather(here::here("data/raw_feather/labevents.feather"))

#Lab Item Definitions
d_labitems <- read_feather(here::here("data/raw_feather/d_labitems.feather"))

#Admissions
admissions <- read_feather(here::here("data/raw_feather/admissions.feather"))

#Patient
patient <- read_feather(here::here("data/raw_feather/patients.feather"))

# Discharge Diagnosis
diagnoses_icd <- read_feather(here::here("data/raw_feather/diagnoses_icd.feather"))

#ICU Stays
icu_stays <- read_feather(here::here("data/raw_feather/icustays.feather"))

# Microbio
micro_bio <- read_feather(here::here("data/raw_feather/microbiologyevents.feather"))

# Prescriptions
prescriptions <- read_feather(here::here("data/raw_feather/prescriptions.feather"))

# List of Hadm_ID and Readmit_30 After Note Event Drop NA. Check to see the differences
export_from_notes <- read_feather(here::here("data/r_feather_output/export_for_admissions.feather"))
```

# Processing
# Admissions
```{r}
glimpse(admissions)
```

The following actions and transformations are required.
* Add leading zeros for Subject ID to maintain a consistent number of digits
* Row_ID does not link to any other table and can be dropped. 
* The use of "" for NA is replaced with NA
* Date-Time Objects stored as characters converted to Date-Time
* Convert boolean flags to factor
* Convert Admission Location to factor
* Convert HAMID to character.
* Replace blank with NA

```{r}
admissions_1 <- admissions %>% 
  select(-row_id) %>% 
  mutate(
    admittime = ymd_hms(admittime),
    dischtime = ymd_hms(dischtime),
    deathtime = ymd_hms(deathtime),
    edregtime = ymd_hms(edregtime),
    edouttime = ymd_hms(edouttime)
  ) %>% 
  mutate(
    hospital_expire_flag = as.factor(hospital_expire_flag),
    has_chartevents_data = as.factor(has_chartevents_data)
    
  ) %>% 
  mutate(
    subject_id = as.character(subject_id),
    hadm_id  =as.character(hadm_id)
  ) %>% 
  mutate(
    language = na_if(language,""),
    religion  = na_if(religion ,""),
    marital_status  = na_if(marital_status ,"")
    )

# Reinstate leading zeros for Subject_ID
admissions_1$subject_id  <- str_pad(
  string = admissions_1$subject_id, 
  width = 5, 
  side = "left", 
  pad = "0")
```

```{r}
admissions_1 %>% 
  head(10) 
```

```{r}
#describe(admissions_1)
```

```{r}
#skim(admissions_1)
```

Patient Information is also required. The following data from the Patients table will be joined with the admission table. Several transformations are required before joining the data frames.

* Convert Date of Birth to Date Time
* Convert Gender to Factor
* Pad leading zeros to subject_id

```{r patient_transformation}
patient_1 <- patient %>% 
  select(subject_id:dob) %>% 
  mutate(
    gender = as.factor(gender),
    dob = as_date(ymd_hms(dob)), 
    subject_id = str_pad(
      string = subject_id, 
      width = 5, 
      side = "left", 
      pad = "0"
    )
  )
```

The admission and patient data frame are joined on subject_id
```{r patient_admission_join}
admissions_2 <- admissions_1 %>% 
  left_join(patient_1, by = "subject_id")
```


```{r inspect_join}
#describe(admissions_2)
```

The following processing will be performed on the dataset:

Drop

* Type = Newborn
* Death = Yes
* Language
* Religion
* edouttime
* edregtime 
* diagnosis

Modify

* Missing Marital Status to New Variable

Create

* Calculate Length of Stay. Filter out if less than zero. This is assumed to be an error.
* Calcuate Age at Admission


```{r}
admissions_2 %>% 
  mutate(
    admitdate = as_date(admittime),
    age = round(time_length(difftime(time1 = admitdate, time2 = dob, units = "days"), unit = "years"),1)
  ) %>% 
  select(dob, admitdate, admittime, age) %>% 
  arrange() %>% 
  ggplot(mapping = aes(x = "", y = age)) + 
  geom_violin()
```


```{r}
admissions_3 <- admissions_2 %>% 
  select(-c(edregtime, edouttime, language, religion, deathtime, diagnosis)) %>% 
  filter(hospital_expire_flag == 0) %>% 
  filter(admission_type != "NEWBORN") %>% 
  select(-hospital_expire_flag) %>% 
  mutate(
    age_yr = round(time_length(difftime(time1 = as_date(admittime), time2 = dob, units = "days"), unit = "years"),1),
    length_stay_hr = round(as.numeric(difftime(time1 = dischtime, time2 = admittime, units = "hours")),1),
    marital_status = replace_na(data = marital_status, replace = "MISSING")
  ) %>% 
  filter(length_stay_hr > 0)
         
describe(admissions_3)
```

```{r age_hist}
ggplot(data = admissions_3,
       aes(x = age_yr)) + 
  geom_density()
```


Next we need to determine if and when a persons next visit was, and how long between visits.

* **next_admit_dt**: If a subject_id has multiple visits, this is the next visit date and time.
* **next_admit_type**: The type of visit.
* **admit_delta**: Length of time between visits
* **readmit_30**: Yes, if admit_delta is < 30 days

```{r}
admissions_4 <- admissions_3 %>% 
  group_by(subject_id) %>% 
  mutate(
    next_admit_dt = lead(admittime, order_by = admittime),
    next_admit_type = lead(admission_type, order_by = admittime),
    admit_span_days = round(as.numeric(difftime(time1 = next_admit_dt, time2 = admittime, units = "days")),1),
    readmit_30 = case_when(
      admit_span_days > 30 & next_admit_type != 'ELECTIVE' ~ 0,
      admit_span_days <= 30 & next_admit_type != 'ELECTIVE' ~ 1
    ),
    readmit_30 = replace_na(readmit_30,0)
  ) %>% 
  select(-c(admittime, dischtime, dob, next_admit_dt:admit_span_days)) %>% 
  ungroup()

admissions_4$readmit_30 <- as.factor(admissions_4$readmit_30)
```

```{r}
describe(admissions_4)
```

We will now add IUC stay information. The ICU stay table will be joined to the Admission table. If there is an ICU stay there will be an icustay_id associated with an hamdid. If the join returns NA there is no ICU stay.
```{r icu_join}
#Prepare ICU data frame
icu_stays_1 <- icu_stays %>% 
  select(hadm_id) %>% 
  mutate(
    hadm_id = as.character(hadm_id),
    ) %>% 
  distinct(hadm_id) %>% 
  mutate(
    icu_stay = (1)
  )

icu_stays_1

admissions_5 <- admissions_4 %>% 
  left_join(icu_stays_1, by = "hadm_id") %>%
  mutate(icu_stay = replace_na(data = icu_stay, replace = 0)) %>% 
  mutate(icu_stay = as.factor(icu_stay))
  
glimpse(admissions_5)

skim(admissions_5)
```

```{r}
skim(admissions_5)
```



List of subjects with multiple admissions and admission count.
```{r}
admissions_5 %>% 
  filter(readmit_30 == 1) %>% 
  group_by(subject_id) %>% 
  summarise(n = n()) %>% 
  arrange(desc(n))
```


## Lab Events
```{r}
glimpse(lab_events)
```

The following actions and transformations are required.

* Row_ID does not link to any other table and can be dropped. 
* The remaining ID variables should converted from integer. Subject_ID is set to factor.
* The use of "" for NA is replaced with NA
* charttime converted to date_time object
* Remove quotation marks for value and valueuom

Time zone does not matter. It is assumed every unique visit id is at the same location. We also only care about time duration, so any final time date will be ther difference between to date time values.


```{r}
lab_events_1 <- lab_events %>% 
  select(-row_id) %>% 
  mutate(
    subject_id = str_pad(
      string = subject_id, 
      width = 5, 
      side = "left", 
      pad = "0"
    ),
    hadm_id = as.character(hadm_id),
    itemid = as.character(itemid),
    valueuom = na_if(valueuom, ""),
    flag = na_if(flag, ""),
    charttime = ymd_hms(charttime)
    )
```

```{r}
glimpse(lab_events_1)
```

```{r}
#skim(lab_events_1)
```

Outpatient data is included in the Lab Events table, with hadm_id left blank. These entries will be removed.
```{r}
lab_events_2 <- lab_events_1 %>% 
  drop_na(hadm_id)

glimpse(lab_events_2)
```

With outpatient records removed we will now filter the data frame to only include itemids which we are concerted with.
```{r}
important_features = c(
  "51006", # Urea - Blood
  "51265", # Platelet Count
  "50960", # Magnesium
  "50862", # Albumin
  "50893"  # Calcium
)

lab_events_3 <- lab_events_2 %>% 
  filter(itemid %in% important_features) %>% 
  select(-c(charttime, value, valueuom)) %>% 
  mutate(
    flag = if_else(
      condition = flag == "abnormal", 
      true = 1, 
      false = 0, 
      missing = 0
    ),
    flag = as.character(flag)
  ) %>% 
  drop_na(valuenum)
```

To compute the min, mean, and max of the lab tests we have, I need to convert the data frame from long to wide.
```{r}
# Create Data frame with HADM_ID and Flag
lab_events_flag <- lab_events_3 %>% 
  select(hadm_id, flag) %>% 
  distinct()

#Remove Flag From Lab Events Data Frame
lab_events_3.1 <- lab_events_3 %>%
  select(-flag)

lab_events_4 <- lab_events_3 %>% 
  group_by(subject_id, hadm_id, itemid) %>% 
  mutate(
    #min = min(valuenum),
    #max = mean(valuenum),
    #mean = max(valuenum),
    flag = as.numeric(flag)
  ) %>% 
  ungroup() %>% 
  select(-c(valuenum, subject_id)) %>% 
  distinct()

lab_events_4 %>% head()

skim(lab_events_4)
```

In order for each item_id to be it's own variable we need to pivot this data frame. WE have also grouped by hadm_id and item_id to see which tests had an abnormal reading, and which tests never did. This was determined by summing the number of flags for a hadmid/itemid group. Anything 1 or greater indicates at least one test was abnormal.NA values were replaced with -1.

* 1: Test was taken and at least one abnormal values were observed
* 0: Test was taken and zero abnormal values were observed
* -1: No test was taken

```{r}

lab_events_4.1 <- lab_events_4 %>% 
  group_by(hadm_id, itemid) %>% 
  summarise(flag = sum(flag)) %>% 
  ungroup() %>% 
  mutate(flag = if_else(flag >= 1, 1, 0))

lab_events_4.1

lab_events_5 <- lab_events_4.1 %>%
  pivot_wider(
    names_from = itemid,
    values_from = flag
    ) %>% 
  replace(is.na(.), -1)

lab_events_5 %>% head()

skim(lab_events_5)
```

Join the lab events table to the admissions table. There are additional missing test values. This implies no test of any type was taken for these mospital admissions. These NAs need to be converted to -1.
```{r}
admissions_5.2 <- admissions_5 %>%
  left_join(lab_events_5)

admissions_5.2 %>% skim()

admissions_5.2 %>% head()
```

Join the lab events table to the admissions table. There are additional missing test values. This implies no test of any type was taken for these mospital admissions. These NAs need to be converted to -1. Additinoally, the column names will be renamed to the actual test name.
```{r}
admissions_5.3 <- admissions_5.2 %>% 
  rename(
    albumin = '50862',
    urea ='51006' ,
    platelets = '51265',
    magnesium = '50960',
    calcium = '50893'
    ) %>% 
  replace(is.na(.), -1)

admissions_5.3 %>% skim()
```


### Test Dropping ICU
The folloing gis a test to see how mnay values would still be missing if non-ICU stays were dropped.
```{r}
admissions_5.3 %>% 
  filter(icu_stay == 1) %>% 
  skim()
```


### Test - Comparison
The following is a test using filter to isolate a single of type of test. This is to determine how many people used this test, and compare it to the number of missing values is another project which used this dataset. The current theory is the other project's SQL scripts are wrong.
```{r}
lab_events_4.1 <- lab_events_3.1 %>% 
  select(-subject_id) %>% 
  filter(itemid == "50893") %>% 
  group_by(hadm_id, itemid) %>% 
  mutate(
    #min = min(valuenum),
    mean_50893 = mean(valuenum)
    #max = max(valuenum)
  ) %>% 
  ungroup() %>% 
  select(-c(valuenum, itemid)) %>% 
  distinct()
  
#lab_events_4.1 %>% head()

#glimpse(lab_events_4.1)

admissions_5.1 <- admissions_5 %>%
  left_join(lab_events_4.1, by = "hadm_id")

admissions_5.1 %>% skim()
```


Unfortunately there are too many missing values for many of the tests.
* ..._test_run: Indicates if a test was run
* ..._test_abnormal: If a test is run, was it abnormal


### To Do
* Using filters, check the number of NA returned using the grouping method for one test and compare to the other example.
** Done - Still Returning NAs
* Create boolean category for if a microbiology sample was taken
* Create two boolean values for each lab test, if test was taken, and if flagged.

### Merge Note Events
To create a final set of hadm_ids the Note_Event hadm_id will be joined to the admissions table and NAs will be dropped. Not all observations in the Note Events table had a corresponding hadm_id in the main data frame.

```{r}
export_from_notes_1 <- export_from_notes %>% 
  mutate(dummy = 0) %>% 
select(-readmit_30)


admissions_6 <- admissions_5.3 %>% 
  left_join(y = export_from_notes_1, 
            by = c("hadm_id")) %>% 
  drop_na(dummy) %>% 
  select(-dummy)

admissions_6 %>% skim()
```


The following script creates two variables for lab tests.
```{r}
admissions_7 <- admissions_6 %>% 
  mutate(
    albumin_test = as.factor(if_else(albumin >= 0 , 1, 0)),
    albumin_flag = as.factor(if_else(albumin == 1 , 1, 0)),
    calcium_test = as.factor(if_else(calcium >= 0 , 1, 0)),
    calcium_flag = as.factor(if_else(calcium == 1 , 1, 0)),
    magnesium_test = as.factor(if_else(magnesium >= 0 , 1, 0)),
    magnesium_flag = as.factor(if_else(magnesium == 1 , 1, 0)),
    platelets_test = as.factor(if_else(platelets >= 0 , 1, 0)),
    platelets_flag = as.factor(if_else(platelets == 1 , 1, 0)),
    urea_test = as.factor(if_else(urea >= 0 , 1, 0)),
    urea_flag = as.factor(if_else(urea == 1 , 1, 0))
  ) %>% 
  select(-c(albumin, calcium, magnesium, platelets, urea))

admissions_7 %>% skim()
```

### Micro Bio
```{r}
micro_bio_1 <- micro_bio %>% 
  mutate(hadm_id = as.character(hadm_id))

micro_bio_1 %>% skim()
```

Create a data frame of hadm_ids from the microbiololgy table along with flag variable indicating a microbiology test was taken.
```{r}
micro_bio_2 <- micro_bio_1 %>% 
  select(hadm_id) %>% 
  distinct() %>% 
  mutate(micro_bio_test = 1)

micro_bio_2 %>% skim()
```

Join microbiology table to admissions. Drop dummy.
```{r}
admissions_8 <- admissions_7 %>% 
  left_join(micro_bio_2, by = "hadm_id") %>% 
  mutate(micro_bio_test = as.factor(replace_na(micro_bio_test, 0)))

admissions_8 %>% skim()
```

Drop has_chartevents_data
```{r}
admissions_9 <- admissions_8 %>% 
  select(-has_chartevents_data)
```

## Processing For Python Models
To be used in the machine learning models in python two major changes need to be made:

1. COnvert categorical variales to an n-1 set of binary dummy variables.
2. Convert binary variables currently modeled as factors to integers.

First convert the binary factors to integers. All the factors in the dataframe are binary except gender. In order to use a general function, I converted gender from factor to character first, making all factors in the dataframe binary. Then I converted the binary factors to integers.
```{r}
admissions_10 <- admissions_9 %>% 
  mutate(gender = as.character(gender)) %>% 
  mutate_if(is.factor, as.character) %>% 
  mutate_at(c(seq(12,length(admissions_9),1)), as.integer)
```

Now the Categorical variables need to be converted to dummy binary variables.

* admission_type  
* admission_location
* discharge_location 



```{r}

df_categorical = c(
  "admission_type",
  "admission_location",
  "discharge_location",
  "insurance",
  "marital_status",
  "ethnicity",
  "gender"
)

admissions_11 <- admissions_10 %>% 
  dummy_cols(
    select_columns = df_categorical,
    remove_most_frequent_dummy = TRUE
    ) %>% 
   select(-df_categorical) %>% 
  select(hadm_id, subject_id, readmit_30 , everything())
```

Final inspection of admissions data frame before export.
```{r}
admissions_export <- admissions_11

#admissions_export %>% glimpse()
```
# Export
## Structured Data
```{r}
path <- here::here("data/r_feather_output/df_structured_export.feather")

write_feather(x = admissions_export, path = path)
```

## hadm_id / readmmit_30 For Notes
The processed admisssions data frame is stripped down to the hadm_id and readmit_30 variables. This new data frame is exported to be used with the note_events analysis.
```{r}
admissions__readmit_30 <- admissions_export %>% 
  select(hadm_id, readmit_30)

#admissions__readmit_30 %>% skim()

path <- here::here("data/r_feather_output/export_for_notes.feather")

write_feather(x = admissions__readmit_30, path = path)
```

# Random Tests and Checks
## Check NAs
Atfer processing the Note Events Table, there were about ~2000 less observations than in the processed admissions data frame. The following analysis is to compare the two dataframes to see what the new NAs have in common. If all observations are now ICU stays we may be ablet to use other values.

The skim summary below shows that there are still a large amount of records without and ICU stay. There was not complete overlap, as I was initially curious about.
```{r}
#What happens when you drop all new NAs
admissions_5.2 %>% 
  left_join(y = export_from_notes, 
            by = c("hadm_id")) %>% 
  drop_na() %>% 
  skim()
```

