---
title: "MIMIC III Dataset - Structured Data Analysis"
author: "Evan Canfield"
date: "10/31/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Library
The following are library packages used in this analysis.
```{r library}
if (!require(pacman)) {install.packages('pacman')} 
p_load(
    data.table
  , feather
  , here
  , Hmisc
  , janitor
  , lubridate
  , R.utils
  , skimr
  , stringr
  , tidyverse
)
```

# Set Seed
```{r}
set.seed(5590)
```


# Import
```{r}
#Admissions
admissions <- read_feather(here::here("data/raw_feather/admissions.feather"))
```

# Processing
# Admissions
```{r}
glimpse(admissions)
```


```{r}
admissions_1 <- admissions %>% 
  select(-c(row_id,deathtime, edregtime, edouttime, has_chartevents_data, language, religion, marital_status, admission_location,
            discharge_location, insurance, ethnicity, diagnosis)) %>% 
  mutate(
    admittime = ymd_hms(admittime),
    dischtime = ymd_hms(dischtime)
  ) %>% 
  mutate(
    hospital_expire_flag = as.factor(hospital_expire_flag)
    
  ) %>% 
  mutate(
    subject_id = as.character(subject_id),
    hadm_id  = as.character(hadm_id)
  )

# Reinstate leading zeros for Subject_ID
admissions_1$subject_id  <- str_pad(
  string = admissions_1$subject_id, 
  width = 5, 
  side = "left", 
  pad = "0")
```

```{r}
admissions_1 %>% 
  head(10) 
```

The following processing will be performed on the dataset:

Drop

* Type = Newborn
##* Death = Yes


Create

* Calculate Length of Stay. Filter out if less than zero. This is assumed to be an error.
* Calcuate Age at Admission


```{r}
glimpse(admissions_1)
```

```{r}
admissions_3 <- admissions_1 %>% 
  filter(hospital_expire_flag == 0) %>% 
  filter(admission_type != "NEWBORN") 
         
glimpse(admissions_3)
#describe(admissions_3)
```



Next we need to determine if and when a persons next visit was, and how long between visits.

* **next_admit_dt**: If a subject_id has multiple visits, this is the next visit date and time.
* **next_admit_type**: The type of visit.
* **admit_delta**: Length of time between visits
* **readmit_30**: Yes, if admit_delta is < 30 days

### Updated Method - Back Fill
Did not end up using. There is an error somewhere that is reducing the final number of positives. It should increase it a little.
```{r}
# # Create Dummy Time For Next Appointment
# dummy_time <- ymd_hms("1000-01-01 12:23:34")
# 
# # Next Appointment Flag is for noting which hospital admissions had follow up appointments, but were elective and replaced with NA
# admissions_4 <- admissions_3 %>% 
#   group_by(subject_id) %>% 
#   mutate(
#     next_admit_dt = lead(admittime, order_by = admittime),
#     next_admit_type = lead(admission_type, order_by = admittime)
#   ) %>% 
#   ungroup() %>% 
#   mutate(next_app_flag = case_when(is.na(next_admit_type) ~ 0,
#                                    next_admit_type == 'ELECTIVE' ~ 2,
#                                    TRUE ~ 1)) %>% 
#   select(subject_id:dischtime,admission_type, next_admit_dt:next_app_flag, everything())
# 
#   
# # If Next Appointment is Electve, convert to NA. 
# admissions_4.1 <- admissions_4 %>% 
#   mutate(
#     next_admit_dt = replace_na(next_admit_dt, dummy_time),
#     next_admit_type = na_if(next_admit_type, 'ELECTIVE'),
#     next_admit_dt = if_else(next_app_flag == 2, dummy_time, next_admit_dt),
#     next_admit_dt = na_if(next_admit_dt, dummy_time)
#   )
# 
# # Backfill Remeved Elective Dates.
# # If there is an emergency eevent after an elective event, the emergency time and type will fill that elective space.
# admissions_4.2 <- admissions_4.1 %>% 
#   group_by(subject_id) %>% 
#   fill(next_admit_dt, .direction = "up") %>% 
#   fill(next_admit_type, .direction = "up") %>% 
#   ungroup()
# 
# 
#  #Determine if the next admission qualifies as a Positive Event
# admissions_4.3 <- admissions_4.2 %>%
#   mutate(
#     admit_span_days = round(as.numeric(difftime(time1 = next_admit_dt, time2 = admittime, units = "days")),1),
#     readmit_30 = case_when(admit_span_days <= 30 ~ 1,
#                           TRUE ~ 0
#                           ),
#     readmit_30 = as.factor(readmit_30)
#   ) %>% 
#   select(-next_app_flag) %>% 
#   select(subject_id, hadm_id, readmit_30, everything())
#   
# admissions_4.3 %>% 
#   filter(subject_id=="00339")
# 
# admissions_4.3 %>% describe()

```

### Original Method - No Back Fill
```{r}
admissions_4 <- admissions_3 %>%
  group_by(subject_id) %>%
  arrange(admittime) %>%
  mutate(
    next_admit_dt = dplyr::lead(admittime, order_by = admittime),
    next_admit_type = dplyr::lead(admission_type, order_by = admittime),
    admit_span_days = round(as.numeric(difftime(time1 = next_admit_dt, time2 = dischtime, units = "days")),1),
    readmit_30 = case_when(
      admit_span_days > 30 & next_admit_type != 'ELECTIVE' ~ 0,
      admit_span_days <= 30 & next_admit_type != 'ELECTIVE' ~ 1
    ),
    readmit_30 = replace_na(readmit_30,0)
  ) %>%
  ungroup() %>%
  mutate(readmit_30 = as.factor(readmit_30))

admissions_4 %>% describe()
```

```{r}
ggplot(data = admissions_4, aes(x = admit_span_days)) +
  geom_histogram() +
  xlim(0,365)
```
 
## Processing For Python Models
```{r}
admissions_5 <- admissions_4 %>% 
  mutate(readmit_30 = as.character(readmit_30)) %>% 
  mutate(readmit_30 = as.integer(readmit_30)) %>% 
  select(hadm_id, readmit_30)


skim(admissions_5)
```

## hadm_id / readmmit_30 For Notes
The processed admisssions data frame is stripped down to the hadm_id and readmit_30 variables. This new data frame is exported to be used with the note_events analysis.
```{r}
path <- here::here("data/r_feather_output/export_for_notes.feather")

write_feather(x = admissions_5, path = path)
```
